The intensity of a MC type exercise movement can be measured by the amount of resistance (either body resistance or use of external weights), the volume of repetitions performed and the power or rate at which work is performed. It is our goal to use relatively inexpensive technology, such as the Microsoft Kinect, to measure exerciser’s progress with a reasonable accuracy.
We have met with our fitness experts to create a workout in the style of P90x and Insanity that features exercises that fit the following criteria:
\begin{itemize}
	\item Requires little to no prior skill or training 
	\item Requires strength to accurately achieve the best stance for that particular move
	\item Requires stamina to complete the exercise move at a fast rate.
\end{itemize}
The primary goal of our first set of user studies was to perfect our post processing models and isolate and fix any flaws with the study itself, however, a secondary goal was to collect real data that could inspire our fitness expert benchmark data.  To establish this expert benchmark data set, we used an accumulation of the first set of participants' performance and the knowledge gained from meeting with the experts.  \\
We recorded both the video footage of each participant completing the routine as well as the skeleton and depth sensor data collection tool created to measure factors such as rate of exercise move, body form (predominantly angles between limbs and differences in vertical and horizontal movement), speed, height (where applicable), the duration and frequency of resting time, and the volume of repetitions performed.  We then calculated a score or percentage of the expert benchmark using the collected data as well as generating more granular data specific to each workout move completed.  After the participant has finished the workout, we showed them two different reports 1.) The expert percentage score and 2.) The granular exercise move specific report and ask them to determine which report would be most helpful for them in terms of tracking their performance from workout to workout.