When presented with the two different forms of feedback (design A being the percentage expert score feedback design and design B being the granular workout move specific design),  15 participants (75\%) indicated that they preferred design B to track their performance from workout to workout and 5 participants (25\%) indicated that they preferred design A to track their performance.  The average expert score among participants who chose design A was 44.828 and the average expert score among participants who chose design B was 44.145, which does not prove our hypothesis that those you performed better would like to see less data.  The average expert score adjusted for form among participants who chose design A was 992.402, however, excluding the outlier (participant 5921 performed at 4719.3\% the expert rate), the average was 60.678.  The average export score adjusted for form within participants who chose design B was 51.509.  Some of the reasons given to prefer design B over design A include the approval of the inclusion of the specific workout details.  Participants found it useful to see the areas in which they needed the most improvement as they were unsure of the specifics of their form.  However, one participant indicated that she preferred design A because she was already cognizant of her form and would prefer a tangible number to serve as an incentive for improvement.  Three participants indicated that they would have preferred a synthesis of the two reports and found much of the information portrayed in design B to excessive, however they still preferred design B as design A did not include enough information for them to accurately reflect on their performance.

